Effect of Black Hole Spins on Christodoulou Memory in Binary Mergers and its implication on Observing Gravitational Wave Bursts With Memory in Pulsar Timing Array

### 2019-10-03 notes/Paper.tex
made some changes in the notes

\title{Effect of Black Hole Spins on Christodoulou Memory in Binary Mergers and it's implication on Observing Gravitational Wave Bursts With Memory in Pulsar Timing Array}
\author{Ashok Choudhary}\email{aschoudhary@mix.wvu.edu}
\author{Sean T. McWilliams}\email{sean.mcwilliams@mail.wvu.edu}
\affiliation{Department of Physics and Astronomy, West Virginia University, Morgantown, WV 26506, USA}
\affiliation{Center for Gravitational Waves and Cosmology, West Virginia University, Chestnut Ridge Research Building, Morgantown, WV 26505, USA}

@@

\begin{figure}
	\includegraphics[width=7.0in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDays.pdf}
	\caption{The top figure the memory growth during two weeks interval of time with solid lines. The dashed line shows the complete memory growth. The dashed red line show the memory growth computed using PN}
	\label{fig:resedualGrowth}
\end{figure}

>>>>

\title{Effect of Black Hole Spins on Christodoulou Memory in Binary Mergers and its implication on Observing Gravitational Wave Bursts With Memory in Pulsar Timing Array}
\author{Ashok Choudhary}\email{aschoudhary@mix.wvu.edu}
\author{Sean T. McWilliams}\email{sean.mcwilliams@mail.wvu.edu}
\affiliation{Department of Physics and Astronomy, West Virginia University, Morgantown, WV 26506, USA}
\affiliation{Center for Gravitational Waves and Cosmology, West Virginia University, Chestnut Ridge Research Building, Morgantown, WV 26505, USA}

@@

\begin{figure}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDaysPreFit.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDaysPostfit.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth5YearsDiffSpinsInDaysPrefit.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth5YearsDiffSpinsInDaysPostfit.pdf}
	\caption{The top figure the memory growth during two weeks interval of time with solid lines. The dashed line shows the complete memory growth. The dashed red line show the memory growth computed using PN}
	\label{fig:resedualGrowth}
\end{figure}
